The development of children's ability to track and predict turn structure in conversation

### 2016-01-08 paper/CasillasFrank-Anticip.tex
Updated figures and tables

\usepackage{graphicx}
\usepackage{lineno}
\usepackage{amssymb}
\usepackage{wrapfig}
\usepackage{subfig}
\usepackage{tipa}
\usepackage{float}
\usepackage{longtable}
\usepackage[section]{placeins}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\textwidth]{figures/E1-samples-by-lang-groups-trans-types.png}
\end{center}
\caption{Anticipatory gaze rates across language condition and transition type for the real (red and blue) and randomly permuted baseline (gray). Vertical bars represent the standard error.} 
\label{fig:E1-randvsreal}
\end{figure}

\begin{table}[h!]
\begin{small}
\begin{center}
  \begin{tabular}{lcccl}
  \textbf{\textit{Children}} &&&& \\
    \hline
                   & Estimate & Std. Error & z value & Pr($>$$|$z$|$)    \\
    \hline
    (Intercept)   &      -0.96146 &   0.84901 & -1.132 & 0.257446 \\    
    Age             &    -0.18268 &   0.17507 & -1.043 & 0.296725   \\  
    LgCond$=$\textit{non-English} &          -3.29347 &   0.96045 & -3.429 & 0.000606 *** \\
    Type$=$\textit{non-Question}          &     -1.10129 &   0.86494 & -1.273 & 0.202925     \\
    Duration      &       3.40169 &   1.22826 &  2.770 & 0.005614  **\\
    Age*LgCond$=$\textit{non-English} &       0.52065 &   0.21190 &  2.457 & 0.014008 ** \\  
    Age*TypeS$=$\textit{non-Question}          & -0.01628 &   0.19437 & -0.084 & 0.933232     \\
    LgCond$=$\textit{non-English}* &     2.68166 &   1.35016 &  1.986 & 0.047013 * \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*LgCond$=$\textit{non-English}* & -0.45632 &   0.30163 & -1.513 & 0.130315  \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    \hline
  &&&& \\
  \textbf{\textit{Adults}} &&&& \\
    \hline
                       &  Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\    
    \hline
    (Intercept)       &        -0.1966 &    0.6942 & -0.283 & 0.776988     \\
    LgCond$=$\textit{non-English}    &             -0.8812 &    0.9602 & -0.918 & 0.358754   \\  
    Type$=$\textit{non-Question}             &        -4.4953 &    1.3139 & -3.421 & 0.000623 *** \\
    Duration          &        -1.1227 &    1.9880 & -0.565 & 0.572238     \\
    LgCond$=$\textit{non-English}* &           3.2972 &    1.6101 &  2.048 & 0.040581 * \\ 
    Type$=$\textit{non-Question} &&&& \\
    LgCond$=$\textit{non-English}* &        1.3626 &    3.0077 &  0.453 & 0.650527     \\
    \hspace*{5mm} Duration &&&& \\
    Type$=$\textit{non-Question}*          &  10.5107 &    3.3459 &  3.141 & 0.001682  ** \\
    \hspace*{5mm} Duration &&&& \\
    LgCond$=$\textit{non-English}* & -6.3156 &    4.4926 & -1.406 & 0.159790 \\    
    Type$=$\textit{non-Question}* &&&& \\
    \hspace*{5mm} Duration &&&& \\
    \hline
  \end{tabular}
\end{center}
  \end{small}
  \caption{Model output for children and adults' anticipatory gaze switches.}
\label{tab:E1-models}
\end{table}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{figures/E2-samples-by-lang-groups-trans-types_mod.png}
\end{center}
\caption{Anticipatory gaze rates across language condition and transition type for the real (blue, dark green, light green, and red) and randomly permuted baseline (gray). Vertical bars represent the standard error.} 
\label{fig:E2-randvsreal}
\end{figure}

@@

\begin{footnotesize}
\begin{longtable}{lcccl}
  \textbf{\textit{Children}} &&&& \\
    \hline
                       & Estimate & Std. Error & z value & Pr($>$$|$z$|$)    \\
    \hline
    (Intercept)                & -3.57414  &   0.48576 &  -7.358 & 1.87e-13 ***    \\
    Age                         & 0.02543 &    0.10260  &  0.248   & 0.8042        \\
    Type$=$\textit{non-Question}                      & -0.81873  &   0.59985 &  -1.365  &  0.1723        \\
    Duration                   &  4.17672  &   0.62446  &  6.689 & 2.25e-11 ***    \\
    Age*Type$=$\textit{non-Question}                &    0.15116   &  0.13643  &  1.108  &  0.2679        \\
	\hline
    Condition$=$\textit{normal}            &  0.36710 &    0.43296 &   0.848  &  0.3965        \\
    Age*Condition$=$\textit{normal}       &   0.12919 &    0.10227  &  1.263  &  0.2065        \\
    Condition$=$\textit{normal}*     &   0.91059  &   0.72095  &  1.263 &   0.2066        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{normal}* &   -0.37542  &   0.16963  & -2.213 &   0.0269 *      \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{prosody}         &   -1.63429  &   0.86390 &  -1.892   & 0.0585 .      \\
    Age*Condition$=$\textit{prosody}       &   0.39317 &     0.18907 &   2.080  &  0.0376 *      \\
    Condition$=$\textit{prosody}*     &  1.77190  &   1.24864  &  1.419 &   0.1559        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{prosody}* &  -0.47057 &    0.28703 &  -1.639 &   0.1011        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{words}            &  -0.26741 &    0.59071 &  -0.453  &  0.6508        \\
    Age*Condition$=$\textit{words}           &   0.13740  &   0.13568   & 1.013  &  0.3112        \\
    Condition$=$\textit{words}*     &   -1.02193  &   1.01227  & -1.010  &  0.3127        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{words}*  &   0.08946  &   0.22349   & 0.400 &   0.6890        \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\

    \hline
  &&&& \\
  \textbf{\textit{Adults}} &&&& \\
    \hline
                       &  Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\    
    \hline
    (Intercept)           &  -3.4557   &   0.7199 &  -4.800 & 1.58e-06 *** \\ 
    Type$=$\textit{non-Question}                  &   0.4292  &    0.6089  &  0.705 & 0.480916     \\ 
    Duration             &     4.7500   &   1.2480  &  3.806 & 0.000141 *** \\ 
	\hline
    Condition$=$\textit{normal}    &      1.2556   &   0.5633  &  2.229 & 0.025805 *   \\ 
    Condition$=$\textit{normal}* &   -0.9452  &    0.7631 &  -1.239 & 0.215475     \\ 
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{prosody}     &     0.3349  &    0.8965  &  0.374 & 0.708692     \\ 
    Condition$=$\textit{prosody}*  &  0.6627  &    1.2138 &   0.546 & 0.585108     \\ 
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{words}       &     1.5938  &    0.7208 &   2.211 & 0.027023 *   \\ 
    Condition$=$\textit{words}*   &  -1.1265  &    0.9109  & -1.237 & 0.216201     \\ 
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    \hline
    &&&& \\
  \caption{Model output for children and adults' anticipatory gaze switches.}
\label{tab:E2-models}
\end{longtable}
\end{footnotesize}

@@

\begin{table}[h]
  \begin{scriptsize}
\centering
  \begin{tabular}{lccccc}
    Variable & Mean & Median & \textit{SD} & Minimum & Maximum\\ 
    \hline
	\textbf{\textit{Children}} &&&&& \\
    \hline
    (Intercept)						&	-2.52 (-458.42)	& -2.54 (-2.86)	& 0.87 (1319.22)		& -5.53 (-8185.36)	& 0.41 (0.97)			\\
    Age								& -0.51 (-17.83)		& -0.49 (-0.53)	& 0.79 (83.78)		& -3.71 (-672.2)		& 2.3 (342.8)			\\
    LgCond					& -0.53 (-109.91)		& -0.55 (-0.63)	& 0.93 (564.42)		& -3.93 (-4418.74)	& 3.23 (2296.19)		\\
    Type							& -0.10 (-29.66)		& -0.09 (-0.1)		& 0.98 (515.12)		& -4.06 (-4383.92)	& 3.23 (2296.19)		\\
    Duration						& 0.99 (345.53)		& 0.98 (1.15)		& 1.07 (1323.13)		& -2.44 (-5048.24)	& 3.36 (3416.68)		\\
    Age*LgCond				& 0.19 (10.64)		& 0.2 (0.18)		& 0.9 (109.6)			& -3.31 (-581.61)		& 5.78 (9985.16)		\\
    Age*Type						& 0.02 (-1.8)			& 0.001 (-0.05)	& 0.9 (98.27)			& -3.36 (-884.36)		& 3.59 (946.81)		\\
    LgCond*Type			& 0.2 (45.32)			& 0.2 (0.27)		& 0.96 (691.3)		& -3.12 (-4160.06)	& 3.45 (640.43)		\\
    Age*LgCond*Type		& -0.12 (-14.23)		& -0.12 (-0.15)	& 0.93 (156.72)		& -2.98 (-1318.26)	& 3.39 (5107.64)		\\
    \hline
	\textbf{\textit{Adults}} &&&&& \\
    \hline
    (Intercept)    					&    -1.63 (-126.14) 	& -1.71 (-1.73)	& 0.97 (713.39)		& -4.08 (-12111.22)	& 2.15 (649.55)		\\
    LgCond  					&      -0.26 (-679.6) 	& -0.3 (-0.53)		& 1.02 (15894.33)	& -3.45 (-494979.7)	& 3.35 (88581.58)	\\
    Type 							&       -0.11 (6.29) 	& -0.13 (-0.04)	& 1.11 (501.5)		& -3.85 (-6420.76)	& 3.28 (8177.88)		\\
    Duration  						&       0.25 (84.09) 	& 0.27 (0.26)		& 1.1 (1152.94)		& -3.25 (-10864.51)	& 3.46 (18540.62)	\\
    LgCond*Type  			&       0.12 (-242.27) 	& 0.1 (0.34)		& 1.07 (26836.7)		& -3.41 (-62264.27)	& 3.81 (509198.4)	\\
    LgCond*Duration  		&       0.15 (780.03) 	& 0.16 (0.39)		& 1.04 (44105.02)	& -3.84 (-798498.6)	& 3.55 (1145951)		\\
    Type*Duration 				&        0.05 (-6.56) 	& 0.05 (0.02)		& 1.13 (1389.9)		& -3.54 (-15979.22)	& 3.87 (16419.46)	\\
    LgCond*Type*Duration  &      -0.06 (1083.63)	& -0.08 (-0.21)	& 1.1 (63116.54)		& -4.21 (-1201895)	& 4.02 (1284965)		\\
    \hline
  \end{tabular}
  \caption{Estimated \textit{t}-values for each predictor in in the adult and child models from Experiment 1. Converging (`C') and non-converging (`non-C') values are shown as: `C (non-C)'. }
\label{tab:nonconv_e1}
 \end{scriptsize}
\end{table}

>>>>

\usepackage{graphicx}
\usepackage{lineno}
\usepackage{amssymb}
\usepackage{wrapfig}
\usepackage{subfig}
\usepackage{tipa}
\usepackage{float}
\usepackage{longtable}
\usepackage[section]{placeins}
\usepackage{rotating}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\textwidth]{figures/E1-samples-by-lang-groups-trans-types.png}
\end{center}
\caption{Anticipatory gaze rates across language condition and transition type for the real (red and blue) and randomly permuted baseline (gray). Vertical bars represent 95\% confidence intervals.} 
\label{fig:E1-randvsreal}
\end{figure}

\begin{table}[h!]
\begin{small}
\begin{center}
  \begin{tabular}{lcccl}
  \textbf{\textit{Children}} &&&& \\
    \hline
                   & Estimate & Std. Error & z value & Pr($>$$|$z$|$)    \\
    \hline
    (Intercept)   						& -0.96145	& 0.84915		& -1.132	& 0.257531 	\\    
    Age             						& -0.18268	& 0.17509		& -1.043	& 0.296764   	\\  
    LgCond$=$\textit{non-English} 		& -3.29349	& 0.96055		& -3.429	& 0.000606 *** 	\\
    Type$=$\textit{non-Question}          	& -1.10131	& 0.86520		& -1.273	& 0.203055     	\\
    Duration      						& 3.40171		& 1.22878		&  2.768	& 0.005634  **	\\
    Age*LgCond$=$\textit{non-English} 	& 0.52066		& 0.21192		&  2.457	& 0.014015 * 	\\  
    Age*TypeS$=$\textit{non-Question}      & -0.01628	& 0.19442		& -0.084	& 0.933262     	\\
    LgCond$=$\textit{non-English}*		& 2.68171		& 1.35045		& 1.986	& 0.047057 * 	\\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*LgCond$=$\textit{non-English}*	& -0.45633	& 0.30168		& -1.513	& 0.130378  \\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    \hline
  &&&& \\
  \textbf{\textit{Adults}} &&&& \\
    \hline
                       &  Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\    
    \hline
    (Intercept)						& -0.1966		& 0.6945		& -0.283	& 0.777062     	\\
    LgCond$=$\textit{non-English}		& -0.8812		& 0.9607		& -0.917	& 0.359028   	\\  
    Type$=$\textit{non-Question}		& -4.4953		& 1.3147		& -3.419	& 0.000628 *** \\
    Duration						& -1.1227		& 1.9889		& -0.565	& 0.572414     	\\
    LgCond$=$\textit{non-English}*		& 3.2972		& 1.6115		& 2.046	& 0.040747 * 	\\ 
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    LgCond$=$\textit{non-English}*		& 1.3625		& 3.0097		& 0.453	& 0.650749     	\\
    \hspace*{5mm} Duration &&&& \\
    Type$=$\textit{non-Question}*		& 10.5107		& 3.3482		& 3.139	& 0.001694  ** 	\\
    \hspace*{5mm} Duration &&&& \\
    LgCond$=$\textit{non-English}*		& -6.3156		& 4.4969		& -1.404	& 0.160191 	\\    
    \hspace*{5mm} Type$=$\textit{non-Question}* &&&& \\
    \hspace*{5mm} Duration &&&& \\
    \hline
  \end{tabular}
\end{center}
  \end{small}
  \caption{Model output for children and adults' anticipatory gaze switches.}
\label{tab:E1-models}
\end{table}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{figures/E2-samples-by-lang-groups-trans-types.png}
\end{center}
\caption{Anticipatory gaze rates across language condition and transition type for the real (blue, dark green, light green, and red) and randomly permuted baseline (gray). Vertical bars represent 95\% confidence intervals.} 
\label{fig:E2-randvsreal}
\end{figure}

@@

\begin{footnotesize}
\begin{longtable}{lcccl}
  \textbf{\textit{Children}} &&&& \\
    \hline
                       & Estimate & Std. Error & z value & Pr($>$$|$z$|$)    \\
    \hline
    (Intercept)						& -3.49403	& 0.48454		& -7.211	& 5.55e-13 ***    	\\
    Age							& 0.02436		& 0.10249		& 0.238	& 0.8121        		\\
    Type$=$\textit{non-Question}		& -0.88900	& 0.61192		& -1.453	& 0.1463        		\\
    Duration						& 3.94743		& 0.61668		& 6.401	& 1.54e-10 ***    	\\
    Age*Type$=$\textit{non-Question}	& 0.15359		& 0.13996		& 1.097	& 0.2725        		\\
	\hline
    Condition$=$\textit{normal}			& 0.37337		& 0.43421		& 0.860	& 0.3899        		\\
    Age*Condition$=$\textit{normal}		& 0.12950		& 0.10217		& 1.267	& 0.2050        		\\
    Condition$=$\textit{normal}*			& 0.91074		& 0.72581		& 1.255	& 0.2096        		\\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{normal}*		& -0.37965	& 0.17031		& -2.229	& 0.0258 *      		\\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{prosody}			& -1.60734	& 0.86680		& -1.854	& 0.0637 .      		\\
    Age*Condition$=$\textit{prosody}		& 0.39271		& 0.18905		& 2.077	& 0.0378 *      		\\
    Condition$=$\textit{prosody}*		& 1.68552		& 1.05414		& 1.599	& 0.1098        		\\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{prosody}*	& -0.32360	& 0.23229		& -1.393	& 0.1636        		\\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
	\hline
    Condition$=$\textit{words}			& -0.26996	& 0.59313		& -0.455	& 0.6490        		\\
    Age*Condition$=$\textit{words}		& 0.14044		& 0.13565		& 1.035	& 0.3005        		\\
    Condition$=$\textit{words}*			& -1.03066	& 1.01610		& -1.014	& 0.3104        		\\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    Age*Condition$=$\textit{words}*		& 0.08829		& 0.22387		& 0.394	& 0.6933        		\\
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\

    \hline
  &&&& \\
  \textbf{\textit{Adults}} &&&& \\
    \hline
                       &  Estimate & Std. Error & z value & Pr($>$$|$z$|$) \\    
    \hline
    (Intercept)						& -3.3811		& 0.6884		& -4.912	& 9.03e-07 *** 		\\ 
    Type$=$\textit{non-Question}		& 0.4375		& 0.5854		& 0.747	& 0.4549     		\\ 
    Duration						& 4.6961		& 1.1804		& 3.978	& 6.94e-05 *** 		\\ 
	\hline
    Condition$=$\textit{normal}			& 1.2033		& 0.5359		& 2.245	& 0.0247 *   		\\ 
    Condition$=$\textit{normal}*			& -0.9627		& 0.7358		& -1.308	& 0.1907     		\\ 
    \hspace*{5mm} Type$=$\textit{non-Queston} &&&& \\
	\hline
    Condition$=$\textit{prosody}			& 0.2407		& 0.8011		& 0.301	& 0.7638     		\\ 
    Condition$=$\textit{prosody}*		& 0.5525		& 0.9374		& 0.589	& 0.5556     		\\ 
    \hspace*{5mm} Type$=$\textit{non-Queston} &&&& \\
	\hline
    Condition$=$\textit{words}			& 1.5613		& 0.7087		& 2.203	& 0.0276 *   		\\ 
    Condition$=$\textit{words}*			& -1.1557		& 0.8854		& -1.305	& 0.1918     		\\ 
    \hspace*{5mm} Type$=$\textit{non-Question} &&&& \\
    \hline
    &&&& \\
  \caption{Model output for children and adults' anticipatory gaze switches.}
\label{tab:E2-models}
\end{longtable}
\end{footnotesize}

@@

\begin{sidewaystable}[!htbp]
  \begin{scriptsize}
\centering
  \begin{tabular}{lllllllllll}
    Variable 				& Mean-C & Mean-NC & Median-C & Median-NC & \textit{SD}-C & \textit{SD}-NC & Min-C & Min-NC & Max-C & Max-NC \\ 
    \hline
	\textbf{\textit{Children}} &&&&& \\
    \hline
    (Intercept)				& -2.52	& -458.42		& -2.54	& -2.86	& 0.87	& 1319.22		& -5.53	& -8185.36	& 0.41	& 0.97		\\
    Age					& -0.51	& -17.83		& -0.49	& -0.53	& 0.79	& 83.78		& -3.71	& -672.2		& 2.3		& 342.8		\\
    LgCond					& -0.53	& -109.91		& -0.55	& -0.63	& 0.93	& 564.42		& -3.93	& -4418.74	& 3.23	& 2296.19		\\
    Type					& -0.10	& -29.66		& -0.09	& -0.1	& 0.98	& 515.12		& -4.06	& -4383.92	& 3.23	& 2296.19		\\
    Duration				& 0.99	& 345.53		& 0.98	& 1.15	& 1.07	& 1323.13		& -2.44	& -5048.24	& 3.36	& 3416.68		\\
    Age*LgCond				& 0.19	& 10.64		& 0.2		& 0.18	& 0.9		& 109.6		& -3.31	& -581.61		& 5.78	& 9985.16		\\
    Age*Type				& 0.02	& -1.8		& 0.001	& -0.05	& 0.9		& 98.27		& -3.36	& -884.36		& 3.59	& 946.81		\\
    LgCond*Type			& 0.2		& 45.32		& 0.2		& 0.27	& 0.96	& 691.3		& -3.12	& -4160.06	& 3.45	& 640.43		\\
    Age*LgCond*Type		& -0.12	& -14.23		& -0.12	& -0.15	& 0.93	& 156.72		& -2.98	& -1318.26	& 3.39	& 5107.64		\\
    \hline
	\textbf{\textit{Adults}} &&&&& \\
    \hline
    (Intercept)    				& -1.63	& -126.14		& -1.71	& -1.73	& 0.97	& 713.39		& -4.08	& -12111.22	& 2.15	& 649.55		\\
    LgCond  				& -0.26	& -679.6		& -0.3	& -0.53	& 1.02	& 15894.33	& -3.45	& -494979.7	& 3.35	& 88581.58	\\
    Type 					& -0.11	& 6.29		& -0.13	& -0.04	& 1.11	& 501.5		& -3.85	& -6420.76	& 3.28	& 8177.88		\\
    Duration  				& 0.25	& 84.09		& 0.27	& 0.26	& 1.1		& 1152.94		& -3.25	& -10864.51	& 3.46	& 18540.62	\\
    LgCond*Type  			& 0.12	& -242.27		& 0.1		& 0.34	& 1.07	& 26836.7		& -3.41	& -62264.27	& 3.81	& 509198.4	\\
    LgCond*Duration  		& 0.15	& 780.03		& 0.16	& 0.39	& 1.04	& 44105.02	& -3.84	& -798498.6	& 3.55	& 1145951	\\
    Type*Duration 			& 0.05	& -6.56		& 0.05	& 0.02	& 1.13	& 1389.9		& -3.54	& -15979.22	& 3.87	& 16419.46	\\
    LgCond*Type*Duration  	& -0.06	& 1083.63		& -0.08	& -0.21	& 1.1		& 63116.54	& -4.21	& -1201895	& 4.02	& 1284965	\\
    \hline
  \end{tabular}
  \caption{Estimated \textit{t}-values for each predictor in converging (`-C') and non-converging (`-NC') adult and child models from Experiment 1. }
\label{tab:nonconv_e1}
 \end{scriptsize}
\end{sidewaystable}
